Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-01 paper.qmd
Fixed Figure 5

# Changed the axis parameters
axis_obj <- gen_axes(
    proj = model_prj1 * 2,
    limits = 0.8,
    axis_pos_x = -0.4,
    axis_pos_y = -0.4,
    axis_labels = names(scaled_two_curvy_data),
    threshold = 0.05)

@@

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            scaled_data = scaled_two_curvy_data, 
                            scaled_data_model = scaled_two_curvy_data_model, 
                            distance_df_small_edges = distance_df_small_edges_two_curvy, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 6,
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0))

@@

# Changed the axis parameters
axis_obj <- gen_axes(
    proj = model_prj2 * 2,
    limits = 0.8,
    axis_pos_x = -0.3,
    axis_pos_y = -0.3,
    axis_labels = names(scaled_two_curvy_data),
    threshold = 0)

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  projected_df = projected_df, 
  model_df = model_df, 
  axes = axes, 
  circle = circle, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  title = "d", 
  cex = 1, 
  position = sc_ltr_pos,
  axis_text_size = 4, 
  is_category = FALSE) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")

>>>>

# Changed the axis parameters
axis_obj <- gen_axes(
    proj = model_prj1 * 2,
    limits = 0.9,
    axis_pos_x = -0.4,
    axis_pos_y = -0.4,
    axis_labels = names(scaled_two_curvy_data),
    threshold = 0.05)

@@

proj_obj2 <- get_projection(projection = model_prj2, 
                            proj_scale = 1, 
                            scaled_data = scaled_two_curvy_data, 
                            scaled_data_model = scaled_two_curvy_data_model, 
                            distance_df_small_edges = distance_df_small_edges_two_curvy, 
                            axis_param = list(limits = 0.5, 
                                              axis_scaled = 2,
                                              axis_pos_x = -0.3, 
                                              axis_pos_y = -0.3, 
                                              threshold = 0.01))

@@

#Changed the axis parameters
axis_obj <- gen_axes(
    proj = model_prj2 * 2,
    limits = 0.7,
    axis_pos_x = -0.35,
    axis_pos_y = -0.35,
    axis_labels = names(scaled_two_curvy_data),
    threshold = 0.02)

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  projected_df = projected_df, 
  model_df = model_df, 
  axes = axes, 
  circle = circle, 
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5), 
  title = "d", 
  cex = 1, 
  position = sc_ltr_pos,
  axis_text_size = 2, 
  is_category = FALSE) #+
  #geom_segment(
  #  data = model_df, 
  #  aes(
  #    x = proj1_from, 
  #    y = proj2_from, 
  #    xend = proj1_to, 
  #    yend = proj2_to), 
  #  color = "#000000")
